---
title: "Final Project Part 2"
output: github_document
name: "Samir Fidai"
always_allow_html: TRUE
---

```{r setup, include=FALSE}
library(tidyverse)
library(janitor)
library(rvest)
library(lubridate)
```


In this chunk, we scrape the dataset from Wikipedia. 

```{r}
url <- "https://en.wikipedia.org/wiki/List_of_Falcon_9_first-stage_boosters#Block_5"

wiki_page <- read_html(url)

BlockFive_dirty <- wiki_page %>%
  html_elements("table") %>%
  .[[1]] %>%
  html_table()

BlockFive_dirty

```

Using the janitor package, I made the column names cleaner and renamed launch date.

```{r}
BlockFive_clean <- BlockFive_dirty %>%
  clean_names() 
BlockFive_clean <- BlockFive_clean %>%  rename(`launch date` = `launch_date_utc_7`)
  
BlockFive_clean

```







Using the Lubridate Package to add in the dates, also the launches are now a numeric value
```{r}
BlockFive_clean <- BlockFive_clean %>% 
  mutate(`launch date` = str_extract(`launch date`, "[0-9]{1,2}[:space:]{1}[A-Z]{1}[a-z]*[:space:][0-9]{4}"),
         `launch date` = dmy(`launch date`),
         launches = as.numeric(launches))
```


In this chunk, the flight number has been trimmed to get rid of any unwanted values. 
```{r}
BlockFive_clean <- BlockFive_clean %>%
  rename(`flight num` = flight_no_b) %>%
  mutate(`flight num` = str_extract(`flight num`, "[F]{1}[9H]{1}[-]{1}[0-9x]{3}"))
```




In this chunk, the turn around time for the boosters have been trimmed down using str_extract,
and have been converted to a numeric value
```{r}
BlockFive_clean <- BlockFive_clean %>%
  mutate(turnaround_time = str_extract(turnaround_time, "[0-9]*"),
         turnaround_time = as.numeric(turnaround_time))
```


launch_pad was split into two categories; one for the outcome of the launch and the other for the name of the launchpad. 
```{r}
BlockFive_clean <- BlockFive_clean %>%
  mutate(`launch outcome` = str_extract(launch_pad, "[A-Za-z]*"),
         `launch pad` = str_extract(launch_pad, "[0-9]{1,2}[AE]?")) %>%
  select(-launch_pad)
```

In this chunk, landing outcome was split into 2 categories, one for the outcome of the landing and the other for where the rocket booster landed. 

```{r}
BlockFive_clean <- BlockFive_clean %>%
  mutate(`landing outcome` = str_extract(landing_location, "[A-Za-z]*"),
         `landing site` = str_extract(landing_location, "(?<=\\()[A-Z]*[-]?[0-9]*")) %>%
  select(-landing_location)
```


To conclude Part 2, we will make a bar graph using ggplot2 of launch sites

```{r}

BlockFive_clean %>%
  filter(!is.na(`launch pad`)) %>%
  ggplot(aes(`launch pad`)) +
  geom_bar(stat = "count", fill = "white") +
  coord_flip() +
  theme_dark() +
  ggtitle("Launch Sites used by Facon 9 Block 5 Boosters")


```

This concludes Part 2 of the Project.


























