---
title: "Final Project"
output: github_document
name: "Samir Fidai"
always_allow_html: TRUE
---

For the first stage of the final project, I aim to make an interactive map in R using brewery coordinates from the Open Brewery API. 

```{r include=FALSE}
library(tidyverse)
library(rvest)
library(httr)
library(jsonlite)
library(leaflet)
library(broom)
```



In this chunk, I connected to the API, limited my search to just microbreweries, and filtered out all values that did not have a latitude and a longitude. I used a map to create a list of all 84 pages of the API

```{r}
breweries_list <- 1:84 %>% map(function(page) {
  url <- paste0("https://api.openbrewerydb.org/breweries?by_type=micro",
         "&per_page=50&page=",
         page)
  
  url %>%
    fromJSON()%>%
    filter(!is.na(latitude), !is.na(longitude))
  
})

```


In this chunk, I combined all of the elements in the list into a single dataframe consisting of all microbreweries with latitudes and longitutdes. I also converted latitude and longitude to numeric. breweries_data_30 was 30 micobreweries I used to test the initial leaflet map


```{r}
breweries_data <- as.data.frame(do.call(rbind, breweries_list))

breweries_data <- breweries_data %>%
  mutate(latitude = as.numeric(latitude),
         longitude = as.numeric(longitude))

breweries_data_30 <- breweries_data %>% head(n=30) %>%
  select(name, latitude, longitude)
```


In this chunk I create the map using the leaflet package. It is interactive. 

```{r}
map <- leaflet(breweries_data) %>%
  addTiles() %>%
  addMarkers(~breweries_data$longitude, ~breweries_data$latitude,
             popup = breweries_data$name,
             clusterOptions = markerClusterOptions())
map
```

This Concludes Part One of the Project. 












